---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Rbills

<!-- badges: start -->
<!-- badges: end -->


## Overview

`Rbills` helps you scrape information from PDF files. It is desined to scrape only `Rocky Mountain Power` and `Summit Energy` documents.

You can use the `Rbills` package to:

* **get_pdf**: get all files in a directory or get files that you choose in a directory.

* **read_pdf_seg**: read pdf files from Summit Energy documents.

* **read_pdf_rmp**: read pdf files from Rocky Mountain Power documents.

Theses functions are for use only with the data team and no other people.

## Installation

You can install the released version of Rbills from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("Rbills")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("BYUIDSS/Rbills")
```

## Usage

```{r}
library(Rbills)
```

### get_pdf

There are two main ways to use `get_pdf` function:

 * To get all files in a directory, insert path in the function. `choose.file = FALSE` is default. The following code is an example.

```{r}
devtools::load_all()
path <- system.file("data-raw", package = "Rbills", mustWork = TRUE)
get_pdf(path)
```

 * To get files that you choose in a directory, insert path and `choose.file = TRUE`. The following code is an example.
 
```{r}
devtools::load_all()
path <- system.file("data-raw", package = "Rbills", mustWork = TRUE)
get_pdf(path, choose.file = TRUE)
```


### read_pdf_seg

The `read_pdf_seg` function only works for `Summit Energy` documents. This function provides a table of data that fits the template of a given file. The following code is an example.

```{r}
devtools::load_all()

path <- system.file("data-raw", package = "Rbills", mustWork = TRUE)

# Choose 'example_gasbill' file.
x <- get_pdf(path, choose.file = TRUE)

gas_table <- read_pdf_seg(path, x)

head(gas_table)

# If you want to convert to the csv file, use utils::write.csv function. 
# utils::write.csv(gas_table, "gas_table.csv", row.names = FALSE)

```

### read_pdf_rmp

The `read_pdf_rmp` function only works for `Rocky Mountain Power` documents. This function provides a table of data that fits the template of a given file. The following code is an example.


```{r}
devtools::load_all()

path <- system.file("data-raw", package = "Rbills", mustWork = TRUE)

# Choose 'example_powerbill' file.
x <- get_pdf(path, choose.file = TRUE)

# Type Bldg 85, Main Bldg, East Bldg, West Bldg 1, West Bldg 2 when prompt function occurs.
# power_table <- read_pdf_rmp(path, x)

# head(power_table)

# If you want to convert to the csv file, use utils::write.csv function.
# utils::write.csv(power_table, "power_table.csv", row.names = FALSE) 
```
